Title

### 2018-07-31 thesis/paper/paper.tex
Modded distinct values

Modelling the constraint requires a predicate associating the value or the statement with its unit and inequality between every unit and all allowed units. Then a violation can be found by finding all tripleEDB with the constrained property and a unit unequal to all allowed units.

@@

\subsection{Distinct values (Q21502410)}
The distinct values constraints requires two distinct constrained statements with the same value. Inequality needs to be evaluated if two statements with the same value have been found.
\begin{equation*}
\text{req\_inequality}(S, O) \leftarrow \text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \text{tripleEDB}(O, X, \text{propertyConstant}, V)
\end{equation*}
This premise in addition with inequality between the statement IDs can then be used to identify all violations.
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{tripleEDB}(O, X, \text{propertyConstant}, V) \wedge \\
&\text{unequal}(S, O)
\end{split}
\end{equation*}
While it is possible to set this constraint on qualifiers or references, this is currently not done and is thus not evaluated here.

>>>>

Modelling the constraint requires a predicate associating the value or the statement with its unit and inequality between every unit and all allowed units. Then a violation can be found by finding all tripleEDB with the constrained property and a unit unequal to all allowed units. In theory the constraint can also be applied to qualifiers and references by setting the respective value on a constraint scope (P4680) qualifier. However, there is currently no such case and will therefore not be regarded.

@@

\subsection{Distinct values (Q21502410)}
The distinct values constraints requires two distinct constrained statements with the same value. 
While finding constrained statements with the same value is straightforward, violations only occur if the statements are actually different, i.e. have an unequal statement id.
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{tripleEDB}(O, X, \text{propertyConstant}, V) \wedge \\
&\text{unequal}(S, O)
\end{split}
\end{equation*}
While it is possible to set this constraint on qualifiers or references, this is currently not done and is thus not evaluated here.
